Manuscript Figures for Genome Biology

### 2018-07-12 manuscript_figures/manuscript_figures.Rmd
Legend-fu on Figure 4 to reduce white space

```{r Figure2}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)]

@@

```{r, Figure3}
# Figure 3: TPR of methods using by pieces of information used 
Fig3 <- plotsim_average(res5d, met="TPR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, facetMethodType = TRUE)

@@

```{r, Figure 4}
library(SummarizedBenchmark)
library(stringr)

@@

Fig4.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                   "ashq")
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        annotate = "propPossible")
Fig4

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder)
Fig4All
```

@@

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "darkred", 
                         mid = "white", 
                         low = "darkblue", 
                         midpoint = alpha) +
  labs(fill = "Mean FDR")

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                rowOrder = Fig4All.rowOrder,
                annotate = "TPR", excludeMethods = NULL)

ggdraw() +
  draw_plot(pfdr + ylab("") + xlab(""), 0.57, 0, 0.22, 1) +
  draw_plot(ptpr + ylab("") + xlab(""), 0.78, 0, 0.22, 1) +
  draw_plot(Fig4All, 0, 0, 0.60, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.57), c(1, 1), size = 15)
ggsave(file.path(outdir, "Figure4.pdf"), width=14, height=5)

@@

```{r}
library(ggbeeswarm)

@@

```{r, Figure 5}

@@

```{r Figure2.5}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("GWAS", objects) & grepl("maf", objects)] 
res <- readRDS(file=resfile)
assayNames(res) <- "qvalue"
res <- addDefaultMetrics(res)

@@

```{r FigureS7}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5|null5", objects)] 
de5 <- readRDS(file=resfile[grepl("de5", resfile) & !grepl("uninf", resfile)])
de5_uninf <- readRDS(file=resfile[grepl("de5", resfile) & grepl("uninf", resfile)])
null5 <- readRDS(file=resfile[grepl("null5", resfile) & !grepl("uninf", resfile)])
null5_uninf <- readRDS(file=resfile[grepl("null5", resfile) & grepl("uninf", resfile)])
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GWAS") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS1.pdf"), width=5, height=4.5)
```

@@

```{r}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GSEA") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS2.pdf"), width=6, height=4.5)
```

@@

```{r}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("ChIP-Seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=5)
```

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS4.pdf"), width=6, height=5)
```

@@

```{r}
wcs <- which(grepl("scRNAseq", casestudy))
objs <- objects[wcs]
ds <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[1]))
m0 <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[2]))
meth <- unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[1]))
cv <- gsub(".rds", "", unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[2])))

@@

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("Microbiome")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS6.pdf"), width=14, height=6.5)
```

@@

>>>>

```{r Figure2, fig.width = 10, fig.height = 8}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5", objects) & 
                  !grepl("uninf", objects)]

@@

```{r, Figure3, fig.width = 8, fig.height = 4}
# Figure 3: TPR of methods using by pieces of information used 
Fig3 <- plotsim_average(res5d, met="TPR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE, facetMethodType = TRUE)

@@

```{r, Figure 4, fig.width = 9, fig.height = 7}
library(SummarizedBenchmark)
library(stringr)

@@

# not excluding any methods
Fig4All.rowOrder <- c("bonf", "bh", "ihw", "qvalue", "bl", "lfdr",
                  "scott-empirical", "scott-theoretical", "ashq")
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = alpha,
                        excludeMethods = NULL, rowOrder = Fig4All.rowOrder) +
        theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.position = c(0.96, 0.93), legend.justification = c(1, 1),
              legend.background = element_rect(fill = scales::alpha("white", 3/4), color = 'black'),
              legend.direction = "horizontal",
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 9),
              legend.margin = margin(6, 10, 6, 10))

Fig4All
```

@@

```{r, fig.width = 14, fig.height = 5}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )

@@

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "FDR",
                rowOrder = Fig4All.rowOrder, 
                annotate = "FDR", excludeMethods = NULL) +
          scale_fill_gradient2(high = "darkred", 
                         mid = "white", 
                         low = "darkblue", 
                         midpoint = alpha) +
          labs(fill = "Mean FDR") +
          theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1)) +
          ylab("") + xlab("") +  
          theme(plot.margin=unit(c(5.5, 5.5, 30, 5.5), "points"))

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = alpha, xlab = "Comparison",
                fill = "TPR",
                rowOrder = Fig4All.rowOrder,
                annotate = "TPR", excludeMethods = NULL) +
          theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1),
              legend.justification = c(1, 0.5),
              legend.text = element_text(size = 7),
              legend.title = element_text(size = 8),
              legend.margin = margin(1, 1, 1, 1)) +
          ylab("") + xlab("") +  
          theme(plot.margin=unit(c(5.5, 5.5, 30, 5.5), "points"))

ggdraw() +
  draw_plot(pfdr, 0.51, 0, 0.24, 1) +
  draw_plot(ptpr, 0.75, 0, 0.24, 1) +
  draw_plot(Fig4All, 0, 0, 0.5, 1) +
  draw_plot_label(c("A", "B"), c(0, 0.51), c(1, 1), size = 15) +
  draw_plot_label("Simulation", 0.72, 0.06, size =11, fontface = "plain")
ggsave(file.path(outdir, "Figure4.pdf"), width=11, height=5)

@@

```{r, fig.width = 6, fig.height = 4}
library(ggbeeswarm)

@@

```{r, Figure 5, fig.width = 9, fig.height = 7}

@@

```{r Figure2.5,  fig.width = 10, fig.height = 4}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("GWAS", objects) & grepl("maf", objects)] 
res <- readRDS(file=resfile)
assayNames(res) <- "qvalue"
res <- addDefaultMetrics(res)

@@

```{r FigureS7,  fig.width = 10, fig.height = 7}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
resfile <- objects[grepl("yeast", objects) & 
                   grepl("de5|null5", objects)] 
de5 <- readRDS(file=resfile[grepl("de5", resfile) & !grepl("uninf", resfile)])
de5_uninf <- readRDS(file=resfile[grepl("de5", resfile) & grepl("uninf", resfile)])
null5 <- readRDS(file=resfile[grepl("null5", resfile) & !grepl("uninf", resfile)])
null5_uninf <- readRDS(file=resfile[grepl("null5", resfile) & grepl("uninf", resfile)])
excludeSet <- c("unadjusted", "bl-df02", "bl-df04", "bl-df05")

@@

```{r, fig.width = 5, fig.height = 4.5}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GWAS") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS1.pdf"), width=5, height=4.5)
```

@@

```{r,  fig.width = 6, fig.height = 4.5}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("GSEA") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS2.pdf"), width=6, height=4.5)
```

@@

```{r, fig.width = 5, fig.height = 5}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("ChIP-Seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=5)
```

### RNA-seq
```{r, fig.width = 6, fig.height = 5}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), objects) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("RNA-seq") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS4.pdf"), width=6, height=5)
```

@@

```{r, fig.width = 15, fig.height = 6}
wcs <- which(grepl("scRNAseq", casestudy))
objs <- objects[wcs]
ds <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[1]))
m0 <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark-"), 
                      function(x) x[2]))
meth <- unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[1]))
cv <- gsub(".rds", "", unlist(lapply(str_split(m0, pattern = "-"), 
                      function(x) x[2])))

@@

```{r, fig.width = 14, fig.height = 6.5}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset) &
              !grepl("baxter", dataset) )
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = alpha, xlab = "Dataset", 
                Nlabel = FALSE, annotate = "propPossible") + 
  ggtitle("Microbiome")+ 
  theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1))
ggsave(file.path(outdir, "FigureS6.pdf"), width=14, height=6.5)
```

@@

```{r, fig.width = 15, fig.height = 4.25}
objects <- list.files( path, recursive=TRUE, pattern="rds", full.names=TRUE )
